### 2014-01-03 arfi_methods.tex
reminder to include text and figure about rotation setup
more notes to myself in the TO DO
new text regarding prostate probe rotation, etc.

>>>>

3D volumetric imaging data was acquired using mechanical rotation of the ER7B
transducer between sequential imaging frames, sweeping across the lateral
extent of the prostate.  This rotation setup utilized a CIVCO
Micro-Touch\texttrademark stabalizer (CIVCO Medical Solutions, Kalona, IA USA)
that allows for complete 6-axis degrees of freedom for manual positioning of
the transducer to sweep through the entire prostate during imaging.  Sequential
imaging frames were $\sim$ 1-2\degree apart, depending on the absolute size of the
prostate.  A custom optical angular feedback transduction circuit utilizing a
reflective linear strip with 500 lines-per-inch (LPI) resolution (US Digital,
Vancouver, WA, USA) was coupled with a 141 oz-in torque stepper motor with
planetary gearbox (Model \#11YPG202S-LW4-R27, Anaheim Automation, Anaheim, CA,
USA) (Figure~\ref{fig:setup_annotated}) to achieve accurate spatial
localization of the imaging frames in the 3D dataset.

\input{fig_setup_annotated}
